Kids LRTI tracking

### 2020-07-29 lrti_tracking.Rmd
update LRTI tracking

child_home_winter <- rbind(wmt_chw, nn_chw, ak_chw) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         paul_lrti = AnyARI) %>% 
  select(area, home_winter_id, child_id_num, paul_lrti, paul_comments) %>% 
  filter(paul_lrti %in% c("Yes", "Debating"))

@@

  select(area, child_id_num, home_winter_id, paul_lrti, paul_comments) %>% 
  arrange(area, child_id_num)

#  filter(visit_date > "2018-06-01") # filter for newer data by date

# write_rds(lrti_diagnosis_data, "Output/lrti_diagnosis_data.rds")
# write_csv(lrti_diagnosis_data, "Output/lrti_diagnosis_data.csv", na = " ")
```

>>>>

child_home_winter <- rbind(wmt_chw, nn_chw, ak_chw) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         paul_lrti = AnyARI) %>% 
  select(area, home_winter_id, child_id_num, paul_lrti, paul_comments)  
  #filter(paul_lrti %in% c("Yes", "Debating"))

@@

  select(area, home, child_id_num, home_winter_id, winter_id, 
         paul_lrti, paul_comments,
         visit_date:treatment_assigned) %>% 
  mutate(child_id_num = as.numeric(child_id_num),
         home_winter_id = as.numeric(home_winter_id)) %>% 
  arrange(area, child_id_num, home_winter_id)

write_rds(lrti_diagnosis_data, paste0(file_path, "Output/lrti_diagnosis_data.rds"))
write_csv(lrti_diagnosis_data, paste0(file_path, "Output/lrti_diagnosis_data.csv", na = " "))

lrti_notes_decisions <- lrti_diagnosis_data %>% 
  distinct(area, child_id_num, home_winter_id, .keep_all = TRUE) %>% 
  select(area, home, child_id_num, home_winter_id, winter_id, 
         paul_lrti, paul_comments) %>% 
  mutate(notes_initial = "",
         start_date_initial = "",
         end_date_initial = "",
         notes_final = "",
         lrti_final = "",
         lrti_start_date_final = "",
         lrti_end_date_final = "")

write_rds(lrti_notes_decisions, paste0(file_path, "Output/lrti_notes_decisions.rds"))
write_csv(lrti_notes_decisions, paste0(file_path, "Output/lrti_notes_decisions.csv", na = " "))
```
